Supplementary Materials: Probing the Deuteron at Very Large Internal Momenta

### 2020-10-21 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
updated supp

\includegraphics[scale=0.22]{plots/coin_and_eCal_CUT_80MeV_35deg.png}

@@

at least 3 out of 4 scintillator planes between both spectrometers. The spectrum is very clean as the typical 2 ns beam bunch structure due to accidental
coincidences is not observed. The out-of-time events observed at the tails can originate from the radiation in the Hall partially entering the detector huts and forming
a trigger in coincidence with the other arm. Figure \ref{fig:coin_ecal_cuts} (right) shows a particle identification cut on the SHMS calorimeter total energy

@@

\includegraphics[scale=0.22]{plots/collimator_CUT_80MeV_35deg_data.png}

@@

Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data yield. The uncertainty in the radiative
correction factor was determined by the Monte-Carlo statistics from the simulation. The large uncertainty in the lowest momentum bin, $p_{\mathrm{r}} = 0.02\pm0.02$, can
be understood from the fact that statistics were limited in this phase space region as indicated by the "hole" observed at $p_{\mathrm{r}} = 0.02$ in Fig. \ref{fig:Pm_Ps} (right). 

@@

\includegraphics[scale=0.26]{plots/RC_factor.png}

@@

Fig. \ref{fig:BC_factor}. The calculation was done using the Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data cross section. The
uncertainty in the bin-centering correction factor was determined from the standard error propagation of a ratio between two quantities. 
\includegraphics[scale=0.26]{plots/BC_factor.png}

@@

>>>>

\includegraphics[scale=0.23]{plots/coin_and_eCal_CUT_80MeV_35deg.png}

@@

at least 3 out of 4 scintillator planes between both spectrometers. The spectrum is very clean as the typical 4 ns beam bunch structure due to accidental
coincidences is not observed. Figure \ref{fig:coin_ecal_cuts} (right) shows a particle identification cut on the SHMS calorimeter total energy

@@

\includegraphics[scale=0.24]{plots/collimator_CUT_80MeV_35deg_data.png}

@@

Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data yield. \\
\indent The uncertainty in the radiative
correction factor was determined for each ($\theta_{nq}$, $p_{\mathrm{r}}$) bin by the Monte-Carlo statistics from the simulation and was propagated to the final cross section error.
The large uncertainty in the lowest momentum bin, $p_{\mathrm{r}} = 0.02\pm0.02$, can be understood from the fact that statistics were limited in this phase space region as indicated by
the "hole" observed at $p_{\mathrm{r}} = 0.02$ in Fig. \ref{fig:Pm_Ps} (right). 

@@

\includegraphics[scale=0.27]{plots/RC_factor.png}

@@

Fig. \ref{fig:BC_factor}. The calculation was done using the Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data cross section. \\
\includegraphics[scale=0.27]{plots/BC_factor.png}

@@

\indent The uncertainty in the bin-centering correction factor was determined for each  ($\theta_{nq}$, $p_{\mathrm{r}}$) bin
using the standard error propagation for a ratio of two quantities and the result was propagated to the final cross section error. \\
